Your Paper Title

### 2025-05-30 Master Thesis/thesis.tex
New

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\usepackage{float}
\usepackage{tikz}
\usepackage{bm}
\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\newcommand{\asbra}[3]{\langle #1 | #2 |#3 ]}
\onehalfspacing

@@

    \textbf{Affiliation:} \\
    Department of Physics, Faculty of Science \\
    Nagoya University \\[1cm]

@@

In conclusion, the results presented here set the foundation for future explorations into more complex (De)constructed models and their gravitational counterparts. These studies promise to deepen our understanding of amplitude structures, dimensional emergence, and the broader implications of gauge-gravity dualities.

\addcontentsline{toc}{section}{References}
\bibliographystyle{unsrt}
\bibliography{reference.bib}

>>>>

\documentclass[12pt]{article}
\usepackage[a4paper, top=2.5cm, bottom=2.5cm, left=2cm, right=2cm]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{cite}
\usepackage{hyperref}
\usepackage{setspace}
\usepackage{lmodern}  % 可选：提高 PDF 输出质量
\usepackage{indentfirst}
\usepackage{cancel}
\usepackage{xcolor}
\usepackage{float}
\usepackage{tikz}
\usepackage{bm}
\usepackage{esvect} % 在导言区加入

\numberwithin{equation}{section}
\newcommand{\mdavg}[2]{\langle #1 \rangle\!\langle #2 \rangle}
\newcommand{\avg}[1]{\langle #1 \rangle}
\newcommand{\aket}[1]{|#1\rangle}
\newcommand{\asqu}[1]{{\langle#1\rangle}^2}
\newcommand{\sket}[1]{|#1]}
\newcommand{\cbrak}[2]{\avg{#1}\![#2]}
\newcommand{\acbrak}[2]{[#1]\!\avg{#2}}
\newcommand{\tif}[1]{\textit{\textbf{#1}}}
\newcommand{\asbra}[3]{\langle #1 | #2 |#3 ]}
\newcommand{\casbra}[3]{[ #1 | #2 | #3 \rangle]}
\newcommand{\bra}[1]{\langle #1|}
\onehalfspacing

@@

    \textbf{Affiliation:} \\
    Theoretical Elementary Particle Physics Laboratory\\
    Department of Physics, Faculty of Science \\
    Nagoya University \\[1cm]

@@

In conclusion, the results presented here set the foundation for future explorations into more complex (De)constructed models and their gravitational counterparts. These studies promise to deepen our understanding of amplitude structures, dimensional emergence, and the broader implications of gauge-gravity dualities.
\newpage
\appendix
\section{Conventions}

In this paper we follow the mostly minus convention $(+, -, -, -)$, and an on-shell momentum satisfies $p^2 = m^2$. The sigma matrix are defined as
\begin{equation}
    \sigma^\mu=(1,\vec{\sigma}),\qquad \bar{\sigma}^\mu=(1,-\vec{\sigma}).
\end{equation}
The corressponding matrix form can be written like 
\begin{equation}
    p_{\alpha\dot{\alpha}}=p_\mu \sigma^\mu=\begin{pmatrix}
        E-p_3 & -p_1+ip_2 \\
        -p_1-ip_2 & E+p_3
    \end{pmatrix}
\end{equation}
and 
\begin{equation}
    p^{\dot{\alpha}\alpha}=p_\mu \bar{\sigma}^\mu=\begin{pmatrix}
        E+p_3 & p_1-ip_2 \\
        p_1+ip_2 & E-p_3
    \end{pmatrix}.
\end{equation}
Then it is easy to obtain their product 
\begin{align}
    p_{\alpha\dot{\alpha}}\cdot p^{\dot{\alpha}\beta}&=\begin{pmatrix}
        E-p_3 & -p_1+ip_2 \\
        -p_1-ip_2 & E+p_3
    \end{pmatrix}
    \begin{pmatrix}
        E+p_3 & p_1-ip_2 \\
        p_1+ip_2 & E-p_3
    \end{pmatrix}\notag\\
    &=\begin{pmatrix}
        E-p^2 & 0 \\
        0 & E-p^2 
    \end{pmatrix}=m^2\delta_\alpha^\beta,
    \label{A.4}
\end{align}
and 
\begin{equation}
    \mathrm{det}p_{\alpha\dot{\alpha}}=m^2.
\end{equation}
We list the following properties for sigma matrix
\begin{gather}
    (\bar{\sigma})^{\dot{\alpha}\alpha}=\varepsilon^{\alpha\beta}\varepsilon^{\dot{\alpha}\dot{\beta}}(\sigma)_{\beta\dot{\beta}}\\
    (\sigma)_{\alpha\dot{\alpha}}(\sigma)_{\beta\dot{\beta}}=2\varepsilon_{\alpha\beta}\varepsilon_{\dot{\alpha}\dot{\beta}}\\
    (\sigma^\mu\bar{\sigma}^\nu+\sigma^\nu\bar{\sigma}^\mu)_\alpha^{\phantom{a}\beta}=2\eta^{\mu\nu}\delta_\alpha^{\phantom{a}\beta}\\
    \mathrm{Tr}(\sigma^\mu\bar{\sigma}^\nu)=\mathrm{Tr}(\bar{\sigma}^\mu\sigma^\nu)=2\eta^{\mu\nu} \label{A.9} 
\end{gather}

The Gamma matrices are defined like
\begin{equation}
    \gamma^\mu=\begin{pmatrix}
        0 & (\sigma)_{\alpha\dot{\alpha}}\\
        (\bar{\sigma})^{\dot{\alpha}\alpha} & 0 
    \end{pmatrix}, \qquad \{\gamma^\mu,\gamma^\nu\}=2\eta^{\mu\nu}
\end{equation}
The $\mathrm{SL}(2,\mathbb{C})$ and $\mathrm{SU}_L(2)$ indices are raised and lowered as
\begin{equation}
    \psi_\alpha = \psi^\beta \varepsilon_{\alpha\beta}, \quad
    \psi^\alpha = \varepsilon^{\alpha\beta} \psi_\beta, \quad
    \varepsilon^{\alpha\beta} \varepsilon_{\beta\gamma} = \delta^\alpha_\gamma
\end{equation}
where the $\psi$ refers to a Weyl spinor belonging to $SU(2)_L$ representation (left-handed spinor), and it is same for $SU(2)_R$ (right-handed spinor).  We use $\varepsilon_{\alpha\beta} = -\varepsilon^{\alpha\beta} = \begin{pmatrix} 0 & -1 \\ 1 & 0 \end{pmatrix}$, the anti-symmetric tensor, to rasie and lower the index. 
More general for eqution \eqref{A.4}, two different spinor contraction can be converted to vector contraction following
\begin{equation}
    p_1^{\alpha \dot\alpha} p_{2 \alpha \dot\alpha} = 2 p_1^\mu p_{2\mu}, 
\end{equation}
where we use the formula \eqref{A.9} and hence for massive momenta, $p^{\alpha\dot\alpha} p_{\alpha\dot\alpha} = 2m^2$, it can also be noticed from \eqref{A.4}. The vector indices are converted to spinorial ones for massive case as:
\begin{equation}
    \gamma^\mu =
    \begin{pmatrix}
        0 & \sigma^\mu_{\alpha\dot\beta} \\
        \bar{\sigma}^\mu{}^{\dot\alpha\beta} & 0
    \end{pmatrix}
    \quad \rightarrow \quad 
    (\bcancel{p} + m) =
    \begin{pmatrix}
        m \delta^\beta_\alpha & p_{\alpha \dot\beta} \\
        p^{\dot\alpha \beta} & m \delta^{\dot\alpha}_{\dot\beta}
    \end{pmatrix}
\end{equation}

For convenience, we also collect some useful identities for spinor-helicity variable:
\begin{gather}
    [p|_{\dot{\alpha}}=\varepsilon _{\dot{\alpha}\dot{\beta}}\sket{p}^{\dot{\beta}},\qquad \langle p|^\alpha=\varepsilon^{\alpha\beta}\aket{p}_{\beta}, \notag \\
    \sket{p}^{\dot{\alpha}}=\varepsilon^{\dot{\alpha}\dot{\beta}}[p|_{\dot{\beta}},\qquad \aket{p}_\alpha=\varepsilon^{\alpha\beta}\langle p|_\beta, \notag \\
    p_{\alpha\dot{\alpha}}=\aket{p}_\alpha[p|_{\dot{\alpha}},\qquad p^{\dot{\alpha}\alpha}=\sket{p}^{\dot{\alpha}}\langle p|^{\alpha}, \notag \\
    \bcancel{p}=\aket{p}_\alpha[p|_{\dot{\alpha}}+\sket{p}^{\dot{\alpha}}\langle p|^{\alpha}, \notag \\
    \avg{pq}=\langle p|^{\alpha}\aket{q}_{\alpha},\qquad [pq]=[p|_{\dot{\alpha}}\sket{q}^{\dot{\alpha}}, \notag \\
    \cbrak{pq}{qp}=2p\cdot q= (p+q)^2 \quad , \notag \\
    (\text{the last equality only holds for massless particle}) \notag \\
    \casbra{k}{\sigma^\mu}{p}=\asbra{p}{\sigma^\mu}{k},\qquad \casbra{k}{\sigma^\mu}{p}=\asbra{k}{\sigma^\mu}{p} ~(\text{for real moemnta}), \notag \\
    \asbra{p}{P}{k}=\langle p|^\alpha P_{\alpha\dot{\alpha}}|k]^{\dot{\alpha}},\qquad \avg{p|y_1y_2|k}=\langle p|^\alpha y_{1\alpha\dot{\alpha}}y_2^{\dot{\alpha}\beta}|p\rangle_\beta, \notag \\
    \asbra{p}{q}{k}=\cbrak{pq}{qk},\qquad \langle 1 | \gamma^\mu | 2 ] \langle 3 | \gamma_\mu | 4 ] = 2 \langle 13 \rangle [24].
\end{gather}

 The analytic continuation are choosen like 
 \begin{equation}
    \aket{-p}=-\aket{p},\qquad \sket{-p}=+\sket{p}.
 \end{equation}

 The angle spinor and square spinor are related by complex conjugation:
 \begin{equation}
        [p|_{\dot{\alpha}}=(\aket{p}_\alpha)^*,\qquad \langle p|^{\alpha}=(\sket{p}^{\dot{\alpha}})^*
 \end{equation}
for real momenta $p$.

\section{Polarization Vectors}
In quantum field theory, the quantities computed directly from Feynman diagrams, such as \( M^\mu(p, \cdots) \), are Lorentz tensors. However, these objects by themselves do not possess the correct transformation properties to be regarded as physical scattering amplitudes. In particular, they fail to transform appropriately under the little group associated with massless particles.

To bridge this gap, we introduce \emph{polarization vectors} \( \epsilon^\mu_\sigma(p) \), whose role is to carry the correct little group behavior. These vectors transform under Lorentz transformations as
\[
\epsilon^\mu_\sigma(\Lambda p) = \Lambda^\mu_{\ \nu} \, \epsilon^\nu_{\sigma'}(p) \, D_{\sigma'\sigma}(W),
\]
where \( D(W) \) is the representation of the little group element \( W \) associated with the Lorentz transformation \( \Lambda \). In this way, the contraction
\[
\epsilon^\mu_\sigma(p) \, M_\mu(p, \cdots)
\]
transforms correctly as a scalar (or spinor/tensor) amplitude under both Lorentz and little group actions.

It is important to emphasize that in modern amplitude formulations—particularly those employing spinor-helicity variables or on-shell recursion relations—polarization vectors are not fundamental ingredients. Rather, they serve as auxiliary tools to extract the physical content from intermediate Feynman tensor structures. The true scattering amplitude is inherently a little group covariant object, and in spinor-helicity language, this structure is built directly into the helicity-spinor formalism.
In fact, as demonstrated in the main text, one can carry out the entire computation without ever introducing polarization vectors. Nevertheless, in certain contexts, particularly when comparing with Feynman diagrammatic results or for pedagogical clarity, their use remains convenient and insightful.

The external line rule for an outgoing massless spin-1 vector boson is implemented by contracting the amplitude with its polarization vector. In the spinor-helicity formalism, the polarization vectors can be expressed as:
\begin{equation}
\epsilon_-^\mu(p; q) = -\frac{\bra{p} \gamma^\mu \sket{q}}{\sqrt{2} [q\,p]}, \qquad
\epsilon_+^\mu(p; q) = -\frac{\bra{q} \gamma^\mu \sket{p}}{\sqrt{2} \langle q\,p \rangle},
\end{equation}
where \( q \neq p \) is an arbitrary reference spinor. The choice of reference spinor encodes gauge redundancy, and the physical amplitude remains unchanged under shifts of the form
\[
\epsilon^\mu_\pm(p) \to \epsilon^\mu_\pm(p) + C\, p^\mu.
\]

The Weyl equation for massless spinors ensures that \( p_\mu \epsilon^\mu_\pm(p) = 0 \). In practice, the polarization vectors are often written in a spinor outer-product form:
\begin{equation}
\bcancel{\epsilon}_-(p; q) = \frac{\sqrt{2}}{[q\,p]}\left( \sket{p}[q| + \sket{q}[p| \right), \qquad
\bcancel{\epsilon}_+(p; q) = \frac{\sqrt{2}}{\langle q\,p \rangle}\left( \sket{p}\bra{q} + \sket{q}\bra{p} \right).
\end{equation}

This freedom in choosing the reference spinor reflects gauge invariance. It does not affect on-shell amplitudes, due to the Ward identity \( p_\mu A_n^\mu = 0 \). For each external gluon (or massless vector), 
one can freely choose a \( q_i \neq p_i \) for defining its polarization. However, consistency requires that the same \( q_i \) be used across all diagrams within a given process. Importantly, the full physical amplitude remains independent of the reference spinors after summing over diagrams.

We consider a massless four-momentum given by
\[
p^\mu = \left( E,\, E \sin\theta \cos\phi,\, E \sin\theta \sin\phi,\, E \cos\theta \right),
\]
which corresponds to a particle moving at an angle \(\theta\) from the \(z\)-axis and azimuthal angle \(\phi\) in spherical coordinates. In Exercise 2.1, the spinor-helicity variables \(\sket{p}\) and \([p|\) associated with this momentum were constructed explicitly.

In this context, we now relate the spinor-helicity polarization vectors from the previous section to the conventional polarization vectors defined in coordinate space. The standard helicity eigenstate vectors take the form:
\[
\tilde{\epsilon}_\pm^\mu(p) = \pm \frac{e^{\mp i\phi}}{\sqrt{2}}
\left( 0,\; \cos\theta \cos\phi \pm i \sin\phi,\; \cos\theta \sin\phi \mp i \cos\phi,\; -\sin\theta \right).
\]

These expressions clearly show the transverse nature of the polarization with respect to the direction of motion. In the special case where \(\theta = \phi = 0\), i.e., the particle moves along the \(z\)-axis, the polarization vectors reduce to
\[
\tilde{\epsilon}_\pm^\mu(p) = \pm \frac{1}{\sqrt{2}}(0,\, 1,\, \mp i,\, 0),
\]
which correspond to circular polarization in the \(xy\)-plane.

\textbf{Example.} Consider the 3-point QED amplitude \( A_3(f^{h_1} \bar{f}^{h_2} \gamma^{h_3}) \), where \( f = e^- \) and \( \bar{f} = e^+ \) denote the outgoing massless electron and positron, respectively. Let us take the helicities to be \( h_1 = -\tfrac{1}{2} \), \( h_2 = +\tfrac{1}{2} \), and \( h_3 = -1 \). The corresponding Feynman amplitude is given by:

\[
i A_3(f^- \bar{f}^+ \gamma^-) = \bar{u}_-(p_1) \, (ie \gamma_\mu) \, v_+(p_2) \, \epsilon_-^\mu(p_3; q)
\]

Using spinor-helicity variables, this becomes:

\[
= ie \bra{1} \gamma_\mu \sket{2}  \frac{ [3| \gamma^\mu \sket{q} }{ \sqrt{2} [3 q] }
= \sqrt{2} i e \frac{ \langle 13 \rangle [2 q] }{ [3 q] }
\]
where we have applied the Fierz identity in the last step to simplify the spinor contractions.

Hence, the amplitude reduces to:

\[
A_3(f^- \bar{f}^+ \gamma^-) = \tilde{e} \, \frac{ \langle 13 \rangle [2 q] }{ [3 q] }
\]
with the shorthand coupling \( \tilde{e} \equiv \sqrt{2} e \) absorbing the normalization factor into the definition of the coupling constant. This is the reason why we use $\tilde{e}$ instead of e in the main context.

Without doubt, the physical amplitude should not depend on arbitrary reference spinor $q$. To eliminate the reference spinor \( |q] \) appearing in the denominator, we first multiply the amplitude by the identity factor \( \langle 12 \rangle / \langle 12 \rangle \). This transforms the numerator as follows:
\[
\langle 13 \rangle \langle 12 \rangle [2q].
\]

Next, using momentum conservation \( p_2 = -p_1 - p_3 \) and the massless Dirac equation \( \bra{1} p_2 = -\bra{1} (p_1 + p_3) \), we compute:
\[
\langle 12 \rangle [2q] = -\bra{1} p_2 \rvert q] = \bra{1} (p_1 + p_3) \rvert q] = \bra{13} q] = \langle 13 \rangle [3q].
\]

Thus, the numerator becomes \( \langle 13 \rangle^2 [3q] \), and the factor of \( [3q] \) cancels with the same term in the denominator of the original expression.

We are therefore left with a compact expression:
\[
A_3(f^- \bar{f}^+ \gamma^-) = \tilde{e} \, \frac{ \langle 13 \rangle^2 }{ \langle 12 \rangle },
\]
which is manifestly independent of the arbitrary reference spinor \( q \).

\newpage
\addcontentsline{toc}{section}{References}
\bibliographystyle{unsrt}
\bibliography{reference.bib}
